Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-06-01 draft/paper1_jenny.tex
Edit Discussion 1

%% ------------------------------------------------------------------------------------ %% 
\subsection{The ``Two phase'' Formation Scenario of Massive Galaxies and the 
            Build-Up of Outer Halos}
    \label{ssec:twophase}

@@

    State of the art hydrodynamic simulations of massive galaxy formation predict 
    that the fraction of accreted stars should strongly increase with their stellar 
    mass and the ``ex-situ'' component dominate the stellar halo (e.g.
    \citealt{RodriguezGomez2016} \addref{}). 
    This picture is supported by the increasingly more prominent stellar halos in 
    more massive galaxies and the negative color gradients we see in these massive 
    galaxies. 
    The slightly bluer color in their outskirts are consistent with the picture that 
    the stars there are from less massive galaxies on the ``red-squence''.

    Also under this picture, the shape of the stellar halo should keep fossil record

    As for the shape of the stellar halo,

    Tidal shocking and stripping during merger with the cD galaxy: the massive galaxies in the substructure generally interact with the cluster centre and the cD galaxy on near-radial orbits

    % Ellipticity of accreted stars.

    It would be interesting to make detailed comparison with these simulations to see
    if they can reproduce the observed

@@

    Meanwhile, these simulation also point out that the fraction of accreted stars 
    increases steeply with total \mstar{} and that the ``ex-situ'' component
    starts to dominate the \mden{} profiles around $R_{\mathrm{e}}$ for 
    \logms{}$\geq 11.5$ galaxies. 
    In this work, we find that the median \mden{} profiles of \rbcg{} and \nbcg{} 
    samples start to show differences around 15-20 kpc, which is close to 
    their $R_{\mathrm{e}}$. 
    Furthermore, the environmental dependence of our median \mden{} profiles 
    becomes more significant in our highest \mtot{} bin (see Fig \ref{fig:prof_4}). 
    These results all align with the picture that the \mhalo{}-dependence of the 
    \mden{} profiles of massive galaxies is driven by the variations in the 
    ``ex-situ'' component at large radii.

>>>>

%% ------------------------------------------------------------------------------------ %% 
\subsection{The Formation of Massive Galaxies and the Assembly of Outer Halos}
    \label{ssec:twophase}

@@

    State of the art hydrodynamic simulations of massive galaxy formation predict 
    that the fraction of accreted stars should strongly increase with their stellar 
    mass and the ``ex-situ'' component dominate the stellar halo (e.g.
    \citealt{Oser2010, Cooper2013, Dubois2013, LeeYi2013, Hirschmann2015,
    RodriguezGomez2016}). 
    This picture is supported by the increasingly more prominent stellar halos in 
    more massive galaxies and the negative color gradients we see in these massive 
    galaxies. 
    The slightly bluer color in their outskirts are consistent with the picture that 
    the stars there are from less massive galaxies on the ``red-squence''.

    Also under this picture, the shape of the stellar halo should preserve information
    about the merging history and even the dark matter halos. 
    Simulations show that, for slow-rotating massive ETGs experienced multiple 
    minor-mergers, the shape of the stellar and dark matter halos are closely 
    correlated (e.g. \citealt{Wu2014}). 
    However, simulation like the one in \citet{Wu2014} predicts that more massive 
    galaxies should be rounder in the outskirt.
    This difference deserves more investigations using stellar kinematics and 
    simulations. 
    It may reflect the importance of major merger in shaping the most massive 
    galaxies. 
    Major merger with central galaxy of massive halo often happens on near-radial 
    orbits, hence leads to (e.g. \citealt{Murante2007}) radially biassed stellar 
    orbits and more elongated halo.

    At a larger scale, the distribution of satellites in massive halo is known to 
    intrinsically align with the central galaxy (e.g. \citealt{Brainerd2005, 
    Yang2006b, NiedersteOstholt2010, HuangMandelbaum2016}), and the alignment signal
    is stronger for more massive galaxies (e.g. \citealt{Hirata2007}).
    The fact that more massive central galaxies have steeper ellipticity profiles 
    and become increasingly more elongated in the outskirt may help understand 
    the physical causes of the intrinsic alignment. 
    Moreover, the shape of the dark matter halo can now be estimated using both 
    satellite distributions and weak lensing analysis (\citealt{ClampittJain2016}). 
    It is interesting to point out that the most recent measurement by 
    \citet{Shin2017} around SDSS clusters show a halo axis-ratio of ${\sim}0.55$, 
    which is only slightly more elongated than the stellar halo of galaxies in our 
    highest \mtot{} bin.

@@

    Recent hydrodynamic simulations of galaxy formation often separate the stars in 
    galaxy into the \textit{in-situ} and accreted components. 
    In simulation, the \textit{in-situ} component is often defined as the stars formed 
    in the halo of the ``main progenitor''.  
    The spatial distribution, kinematic, and stellar population properties of both 
    components become important theoretical predictions to be examined. 
    Among them, the fraction of the accreted component and its relation with stellar 
    mass is the most fundamental one. 
    However, on the observational side, separation of these two physical components 
    is extremely difficult. 
    So far, we have

    % TODO: Move to Paper II
    %Meanwhile, these simulation also point out that the fraction of accreted stars 
    %increases steeply with total \mstar{} and that the ``ex-situ'' component
    %starts to dominate the \mden{} profiles around $R_{\mathrm{e}}$ for 
    %\logms{}$\geq 11.5$ galaxies. 
    %In this work, we find that the median \mden{} profiles of \rbcg{} and \nbcg{} 
    %samples start to show differences around 15-20 kpc, which is close to 
    %their $R_{\mathrm{e}}$. 
    %Furthermore, the environmental dependence of our median \mden{} profiles 
    %becomes more significant in our highest \mtot{} bin (see Fig \ref{fig:prof_4}). 
    %These results all align with the picture that the \mhalo{}-dependence of the 
    %\mden{} profiles of massive galaxies is driven by the variations in the 
    %``ex-situ'' component at large radii.
